Climatology and trends of extreme precipitation in France: evaluation of an explicit-convection regional climate model

### 2025-12-16 article/fig3.qmd
Cleanup: ignore data and generated artefacts

jour_pluie = assemble_vertical(
  "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/mod_norast.svg",
  "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/obs_norast.svg",
  "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/legend.svg",
  "figures/jour_pluie.svg"
)

mean_pluie_jour = assemble_vertical(
  "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/mod_norast.svg",
  "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/obs_norast.svg",
  "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/legend.svg",
  "figures/mean_pluie_jour.svg"
)

mean_max_pluie_jour = assemble_vertical(
  "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/mod_norast.svg",
  "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast.svg",
  "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend.svg",
  "figures/mean-max_pluie_jour.svg"
)

mean_max_pluie_horaire = assemble_vertical(
  "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/mod_norast.svg",
  "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast.svg",
  "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend.svg",
  "figures/mean-max_pluie_horaire.svg"
)

jour_pluie_diff = assemble_un(
  "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/obs_norast_diff.svg",
  "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/legend_diff.svg",
  "figures/jour_pluie_diff.svg"
)

mean_pluie_jour_diff = assemble_un(
  "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/obs_norast_diff.svg",
  "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/legend_diff.svg",
  "figures/mean_pluie_jour_diff.svg"
)

mean_max_pluie_jour_diff = assemble_un(
  "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
  "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend_diff.svg",
  "figures/mean-max_pluie_jour_diff.svg"
)

mean_max_pluie_horaire_diff = assemble_un(
  "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
  "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend_diff.svg",
  "figures/mean-max_pluie_horaire_diff.svg"
)

@@

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_jour.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_horaire.pdf} \\[-0.5mm]

@@

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/mean-max_pluie_horaire_diff.pdf}
\end{tabular}

\endgroup
```

>>>>

# jour_pluie = assemble_vertical(
#   "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/mod_norast.svg",
#   "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/obs_norast.svg",
#   "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/legend.svg",
#   "figures/jour_pluie.svg"
# )

# mean_pluie_jour = assemble_vertical(
#   "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/mod_norast.svg",
#   "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/obs_norast.svg",
#   "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/legend.svg",
#   "figures/mean_pluie_jour.svg"
# )

# mean_max_pluie_jour = assemble_vertical(
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/mod_norast.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend.svg",
#   "figures/mean-max_pluie_jour.svg"
# )

# mean_max_pluie_horaire = assemble_vertical(
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/mod_norast.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend.svg",
#   "figures/mean-max_pluie_horaire.svg"
# )

# jour_pluie_diff = assemble_un(
#   "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_numday/quotidien/compare_1/sat_99.9/legend_diff.svg",
#   "figures/jour_pluie_diff.svg"
# )

# mean_pluie_jour_diff = assemble_un(
#   "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_mean/quotidien/compare_1/sat_99.0/legend_diff.svg",
#   "figures/mean_pluie_jour_diff.svg"
# )

# mean_max_pluie_jour_diff = assemble_un(
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend_diff.svg",
#   "figures/mean-max_pluie_jour_diff.svg"
# )

# mean_max_pluie_horaire_diff = assemble_un(
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend_diff.svg",
#   "figures/mean-max_pluie_horaire_diff.svg"
# )

@@

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth,            trim=14 0 0 0, clip]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 2.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_horaire.pdf} \\[-0.5mm]

@@

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth,            trim=14 0 0 0, clip]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_horaire_diff.pdf}
\end{tabular}

\endgroup

```

### 2025-12-16 article/fig3_nr.qmd
Cleanup: ignore data and generated artefacts

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \input{macros_fig3.tex}
---

@@

def combined_metrics_df(name_file: str):
    base_dir = Path("../outputs")         # dossier racine à explorer
    csv_paths = list(base_dir.rglob(name_file))

@@

combined = combined_metrics_df("metrics.csv")

@@

# mean_max_pluie_jour = assemble_vertical(
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/mod_norast.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend.svg",
#   "figures/mean-max_pluie_jour.svg"
# )

# mean_max_pluie_horaire = assemble_vertical(
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/mod_norast.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend.svg",
#   "figures/mean-max_pluie_horaire.svg"
# )

@@

# mean_max_pluie_jour_diff = assemble_un(
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_mean-max/quotidien/compare_9/sat_99.0/legend_diff.svg",
#   "figures/mean-max_pluie_jour_diff.svg"
# )

# mean_max_pluie_horaire_diff = assemble_un(
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs/maps/stats_mean-max/horaire/compare_9/sat_99.0/legend_diff.svg",
#   "figures/mean-max_pluie_horaire_diff.svg"
# )

df_mean_max_pluie_horaire_avr = combined.loc[(combined["echelle"] == "horaire") & (combined["season"] == "avr") & (combined["col_calculate"] == "mean-max"), ["n", "r", "me", "delta"]]

df_mean_max_pluie_horaire_mai = combined.loc[(combined["echelle"] == "horaire") & (combined["season"] == "mai") & (combined["col_calculate"] == "mean-max"), ["n", "r", "me", "delta"]]

df_mean_max_pluie_horaire_jui = combined.loc[(combined["echelle"] == "horaire") & (combined["season"] == "jui") & (combined["col_calculate"] == "mean-max"), ["n", "r", "me", "delta"]]

@@

df_mean_max_pluie_jour = combined.loc[(combined["echelle"] == "quotidien") & (combined["season"] == "hydro") & (combined["col_calculate"] == "mean-max"), ["n", "r", "me", "delta"]]

df_mean_max_pluie_horaire = combined.loc[(combined["echelle"] == "horaire") & (combined["season"] == "hydro") & (combined["col_calculate"] == "mean-max"), ["n", "r", "me", "delta"]]

r_jp  = float(df_jour_pluie["r"].iloc[0]);  n_jp  = int(df_jour_pluie["n"].iloc[0])
r_mpj = float(df_mean_pluie_jour["r"].iloc[0]); n_mpj = int(df_mean_pluie_jour["n"].iloc[0])
r_mmj = float(df_mean_max_pluie_jour["r"].iloc[0]); n_mmj = int(df_mean_max_pluie_jour["n"].iloc[0])
r_mmh = float(df_mean_max_pluie_horaire["r"].iloc[0]); n_mmh = int(df_mean_max_pluie_horaire["n"].iloc[0])

me_jp  = float(df_jour_pluie["me"].iloc[0]);  d_jp  = float(df_jour_pluie["delta"].iloc[0])
me_mpj = float(df_mean_pluie_jour["me"].iloc[0]); d_mpj = float(df_mean_pluie_jour["delta"].iloc[0])
me_mmj = float(df_mean_max_pluie_jour["me"].iloc[0]); d_mmj = float(df_mean_max_pluie_jour["delta"].iloc[0])
me_mmh = float(df_mean_max_pluie_horaire["me"].iloc[0]); d_mmh = float(df_mean_max_pluie_horaire["delta"].iloc[0])
```

```{python}
#| include: false
macros = rf"""
\newcommand{{\rJourPluie}}{{{r_jp:.2f}}}
\newcommand{{\nJourPluie}}{{{n_jp:d}}}
\newcommand{{\rMeanPluieJour}}{{{r_mpj:.2f}}}
\newcommand{{\nMeanPluieJour}}{{{n_mpj:d}}}
\newcommand{{\rMeanMaxJour}}{{{r_mmj:.2f}}}
\newcommand{{\nMeanMaxJour}}{{{n_mmj:d}}}
\newcommand{{\rMeanMaxHoraire}}{{{r_mmh:.2f}}}
\newcommand{{\nMeanMaxHoraire}}{{{n_mmh:d}}}
\newcommand{{\meJourPluie}}{{{me_jp:+.2f}}}
\newcommand{{\dJourPluie}}{{{d_jp:+.2f}}}
\newcommand{{\meMeanPluieJour}}{{{me_mpj:+.2f}}}
\newcommand{{\dMeanPluieJour}}{{{d_mpj:+.2f}}}
\newcommand{{\meMeanMaxJour}}{{{me_mmj:+.2f}}}
\newcommand{{\dMeanMaxJour}}{{{d_mmj:+.2f}}}
\newcommand{{\meMeanMaxHoraire}}{{{me_mmh:+.2f}}}
\newcommand{{\dMeanMaxHoraire}}{{{d_mmh:+.2f}}}
"""
with open("macros_fig3.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

\begin{tabular}{>{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}}
\small\bfseries \shortstack{Number of days\\ per year\\ with precipitation} &
\small\bfseries \shortstack{Annual\\ precipitation\\ total} &
\small\bfseries \shortstack{Mean of daily\\ precipitation\\ maxima} &
\small\bfseries \shortstack{Mean of hourly\\ precipitation\\ maxima} \\[-0.5mm]

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth,            trim=14 0 0 0, clip]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 2.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_horaire.pdf} \\[-0.5mm]

\small $r=\ \rJourPluie$ \ (n=\ \nJourPluie) &
\small $r=\ \rMeanPluieJour$ \ (n=\ \nMeanPluieJour) &
\small $r=\ \rMeanMaxJour$ \ (n=\ \nMeanMaxJour) &
\small $r=\ \rMeanMaxHoraire$ \ (n=\ \nMeanMaxHoraire) \\[-0.5mm]

\small $ME=\ \meJourPluie\,\mathrm{d}\,(\mathbf{\dJourPluie}\%)$ &
\small $ME=\ \meMeanPluieJour\,\mathrm{mm/yr}\,(\mathbf{\dMeanPluieJour}\%)$ &
\small $ME=\ \meMeanMaxJour\,\mathrm{mm/day}\,(\mathbf{\dMeanMaxJour}\%)$ &
\small $ME=\ \meMeanMaxHoraire\,\mathrm{mm/h}\,(\mathbf{\dMeanMaxHoraire}\%)$\\[-0.5mm]

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth,            trim=14 0 0 0, clip]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/mean-max_pluie_horaire_diff.pdf}
\end{tabular}

\endgroup

```

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \input{macros_fig3_nr.tex}
---

@@

def combined_metrics_df(name_file: str, base_dir: Path = Path("../outputs")):
    csv_paths = list(base_dir.rglob(name_file))

@@

combined = combined_metrics_df("metrics.csv")
combined_nr = combined_metrics_df("metrics.csv", Path("../outputs_nr10"))

@@

# nr_pluie_jour = assemble_vertical(
#   "../outputs_nr10/maps/gev_zTpa/quotidien/compare_1/sat_99.0/hydro/mod_norast.svg",
#   "../outputs_nr10/maps/gev_zTpa/quotidien/compare_1/sat_99.0/hydro/obs_norast.svg",
#   "../outputs_nr10/maps/gev_zTpa/quotidien/compare_1/sat_99.0/legend.svg",
#   "figures/nr_pluie_jour.svg"
# )

# nr_pluie_horaire = assemble_vertical(
#   "../outputs_nr10/maps/gev_zTpa/horaire/compare_1/sat_99.0/hydro/mod_norast.svg",
#   "../outputs_nr10/maps/gev_zTpa/horaire/compare_1/sat_99.0/hydro/obs_norast.svg",
#   "../outputs_nr10/maps/gev_zTpa/horaire/compare_1/sat_99.0/legend.svg",
#   "figures/nr_pluie_horaire.svg"
# )

@@

# nr_pluie_jour_diff = assemble_un(
#   "../outputs_nr10/maps/gev_zTpa/quotidien/compare_1/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs_nr10/maps/gev_zTpa/quotidien/compare_1/sat_99.0/legend_diff.svg",
#   "figures/nr_pluie_jour_diff.svg"
# )

# nr_pluie_horaire_diff = assemble_un(
#   "../outputs_nr10/maps/gev_zTpa/horaire/compare_1/sat_99.0/hydro/obs_norast_diff.svg",
#   "../outputs_nr10/maps/gev_zTpa/horaire/compare_1/sat_99.0/legend_diff.svg",
#   "figures/nr_pluie_horaire_diff.svg"
# )

@@

r_jp  = float(df_jour_pluie["r"].iloc[0]);  n_jp  = int(df_jour_pluie["n"].iloc[0])
r_mpj = float(df_mean_pluie_jour["r"].iloc[0]); n_mpj = int(df_mean_pluie_jour["n"].iloc[0])

me_jp  = float(df_jour_pluie["me"].iloc[0]);  d_jp  = float(df_jour_pluie["delta"].iloc[0])
me_mpj = float(df_mean_pluie_jour["me"].iloc[0]); d_mpj = float(df_mean_pluie_jour["delta"].iloc[0])

df_jour_nr = combined_nr.loc[(combined_nr["echelle"] == "quotidien") & (combined_nr["season"] == "hydro") & (combined_nr["col_calculate"] == "zTpa"), ["n", "r", "me", "delta"]]

df_horaire_nr = combined_nr.loc[(combined_nr["echelle"] == "horaire") & (combined_nr["season"] == "hydro") & (combined_nr["col_calculate"] == "zTpa"), ["n", "r", "me", "delta"]]

rNRJour  = float(df_jour_nr["r"].iloc[0]);  nNRJour  = int(df_jour_nr["n"].iloc[0])
rNRHoraire = float(df_horaire_nr["r"].iloc[0]); nNRHoraire= int(df_horaire_nr["n"].iloc[0])
meNRJour  = float(df_jour_nr["me"].iloc[0]); meNRHoraire = float(df_horaire_nr["me"].iloc[0])
dNRJour     = float(df_jour_nr["delta"].iloc[0]); dNRHoraire  = float(df_horaire_nr["delta"].iloc[0])
```

```{python}
#| include: false
macros = rf"""
\newcommand{{\rJourPluie}}{{{r_jp:.2f}}}
\newcommand{{\nJourPluie}}{{{n_jp:d}}}
\newcommand{{\rMeanPluieJour}}{{{r_mpj:.2f}}}
\newcommand{{\nMeanPluieJour}}{{{n_mpj:d}}}
\newcommand{{\meJourPluie}}{{{me_jp:+.2f}}}
\newcommand{{\dJourPluie}}{{{d_jp:+.2f}}}
\newcommand{{\meMeanPluieJour}}{{{me_mpj:+.2f}}}
\newcommand{{\dMeanPluieJour}}{{{d_mpj:+.2f}}}
\newcommand{{\rNRJour}}{{{rNRJour:.2f}}}
\newcommand{{\nNRJour}}{{{nNRJour:d}}}
\newcommand{{\rNRHoraire}}{{{rNRHoraire:.2f}}}
\newcommand{{\nNRHoraire}}{{{nNRHoraire:d}}}
\newcommand{{\meNRJour}}{{{meNRJour:+.2f}}}
\newcommand{{\meNRHoraire}}{{{meNRHoraire:+.2f}}}
\newcommand{{\dNRJour}}{{{dNRJour:+.2f}}}
\newcommand{{\dNRHoraire}}{{{dNRHoraire:+.2f}}}
"""
with open("macros_fig3_nr.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

\begin{tabular}{>{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}
                >{\centering\arraybackslash}p{.25\paperwidth}}
\small\bfseries \shortstack{Number of days\\ per year with\\ precipitation} &
\small\bfseries \shortstack{Annual\\ total\\ precipitation} &
\small\bfseries \shortstack{10-year return\\ level of daily\\ precipitation} &
\small\bfseries \shortstack{10-year return\\ level of hourly\\ precipitation} \\[-0.5mm]

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie.pdf} &
\includegraphics[width=\linewidth, trim=14 0 0 0, clip]{figures/mean_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/nr_pluie_jour.pdf} &
\includegraphics[width=\linewidth - 2.5mm, trim=14 0 0 0, clip]{figures/nr_pluie_horaire.pdf} \\[-0.5mm]

\small $r=\ \rJourPluie$ \ (n=\ \nJourPluie) &
\small $r=\ \rMeanPluieJour$ \ (n=\ \nMeanPluieJour) &
\small $r=\ \rNRJour$ \ (n=\ \nNRJour) &
\small $r=\ \rNRHoraire$ \ (n=\ \nNRHoraire) \\[-0.5mm]

\small $ME=\ \meJourPluie\,\mathrm{d}\,(\mathbf{\dJourPluie}\%)$ &
\small $ME=\ \meMeanPluieJour\,\mathrm{mm/yr}\,(\mathbf{\dMeanPluieJour}\%)$ &
\small $ME=\ \meNRJour\,\mathrm{mm}\,(\mathbf{\dNRJour}\%)$ &
\small $ME=\ \meNRHoraire\,\mathrm{mm}\,(\mathbf{\dNRHoraire}\%)$\\[-0.5mm]

\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/jour_pluie_diff.pdf} &
\includegraphics[width=\linewidth, trim=14 0 0 0, clip]{figures/mean_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/nr_pluie_jour_diff.pdf} &
\includegraphics[width=\linewidth - 1.5mm, trim=14 0 0 0, clip]{figures/nr_pluie_horaire_diff.pdf}
\end{tabular}

\endgroup
```

### 2025-12-16 article/fig_AROME_trend_mois.qmd
Cleanup: ignore data and generated artefacts

# trend_pluie_jan = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jan/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_jan.svg",
# )
# trend_pluie_fev = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/fev/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_fev.svg",
# )
# trend_pluie_mar = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mar/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_mar.svg",
# )
# trend_pluie_avr = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/avr/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_avr.svg",
# )
# trend_pluie_mai = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mai/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_mai.svg",
# )
# trend_pluie_jui = assemble( # Juin, fichier FR "jui"
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jui/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_jui.svg",
# )
# trend_pluie_juill = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/juill/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_juill.svg",
# )
# trend_pluie_aou = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/aou/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_aou.svg",
# )
# trend_pluie_sep = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/sep/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_sep.svg",
# )
# trend_pluie_oct = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/oct/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_oct.svg",
# )
# trend_pluie_nov = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/nov/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_nov.svg",
# )
# trend_pluie_dec = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/dec/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_dec.svg",
# )
```

>>>>

trend_pluie_jan = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jan/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_jan.svg",
)
trend_pluie_fev = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/fev/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_fev.svg",
)
trend_pluie_mar = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mar/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_mar.svg",
)
trend_pluie_avr = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/avr/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_avr.svg",
)
trend_pluie_mai = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mai/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_mai.svg",
)
trend_pluie_jui = assemble( # Juin, fichier FR "jui"
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jui/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_jui.svg",
)
trend_pluie_juill = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/juill/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_juill.svg",
)
trend_pluie_aou = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/aou/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_aou.svg",
)
trend_pluie_sep = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/sep/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_sep.svg",
)
trend_pluie_oct = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/oct/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_oct.svg",
)
trend_pluie_nov = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/nov/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_nov.svg",
)
trend_pluie_dec = assemble(
"../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/dec/mod_signif_norast.svg",
"figures/trend_horaire_reduce_pluie_dec.svg",
)
```
